---
title: "Assignment 1"

---
# A


Three project types are available with RStudio Cloud: Jupyter Projects, RStudio Projects, and projects from a Github repository. The ability to teach R and Python in the same cloud-based platform allows instructors to develop coding environments for students. The "new projects" button provides access to several project categories. Jupyter project support is in beta; community forums at community.rstudio.com/c/rstudio-cloud are a good place to share your thoughts.

[video youtube link](<https://www.youtube.com/watch?v=UDuuE6eDNrA&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=88>)

# B
1st difference is variable assignment
```{r}
x <- 10
my_name <- "mert"
```
in python

x = 10
my_name = "mert"


2nd difference is creating lists
```{r}
vector <- c(1, 2, 3)
```
in python 
list = [1, 2, 3]

3rd Function Definitions 

in R  {} for defining the scope of functions, uses the if, else, and while keywords.
in Python colons : and indentation for defining scope, uses if, elif, else, and while keywords.

# c

```{r}

library(dslabs)
nadataset <- na_example
summary(nadataset)


```

```{r}
nadataset[is.na(nadataset)] = 0
nadataset <- as.data.frame(nadataset)
print(nadataset)
```
